---
title: "zjin26_mini-assign06"
author: "Vincent Jin"
date: "2023-04-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ============================================================ 
# 	Mini-assignment # 6
# ============================================================ 

``` {r}
library(tidyverse)
library(data.table)
```

# (1) import the data_pat.csv file as a data.table

``` {r}
file_csv = 'C:/Population Health/pop-health-mini-ass6/data_pat.csv'
dt <- as.data.table(read_csv(file = file_csv))
```

# (2) show the histogram of "cost_current_total"; do you see a pattern?

``` {r}
hist(dt$cost_current_total)
```

***Answer***

The histogram suggested a heavily right skewed 

# (3) add a column to store the log of "cost_future_total" -- call the new column as "cost_future_total_log"

``` {r}
dt[, cost_future_total_log := log(cost_future_total)]
dt
```

# (4) show the histogram of "cost_future_total_log"; do you see a pattern?

``` {r}
hist(dt$cost_future_total_log)
```

# (5) count how many of the "cost_future_total_log" values are "-Inf", and then replace all of them with 0

``` {r}
dt[cost_future_total_log == -Inf, .(ct_Inf = .N)]
dt[cost_future_total_log == -Inf, cost_future_total_log := 0]
```

# (6) show the histogram of "cost_future_total_log" once more; do you see a new pattern?

``` {r}
hist(dt$cost_future_total_log)
```

# (7) save the new data.table as data_pat_log.csv and also data_pat_log.rds, but use "\t" (tab) as the separator

``` {r}
file_csv = 'C:/Population Health/pop-health-mini-ass6/data_pat_log.csv'
file_rds = 'C:/Population Health/pop-health-mini-ass6/data_pat_log.rds'
fwrite(dt, file_csv, sep = "\t")
saveRDS(dt, file_rds) 
```